---
title: "ClassificationRandomForest"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Alright, now let's predict if a room is occupied given a bunch of variables (I'm cheating here... sampled down the data a lot to make the whole process faster... but feel free to use the whole dataset if you have time!)

```{r}
load('occupancy.data') # this is a sampled version of the dataset available at http://archive.ics.uci.edu/ml/datasets/Occupancy+Detection+
```

Training the classification random forest

```{r}
library(caret)

model <- train(
  Occupancy ~ .,
  tuneLength = 1,
  data = occupancy, method = "rf",
  trControl = trainControl(method = "cv", number = 2, verboseIter = TRUE)
)
```

Saving it to PMML (what I'm going to use in the C# of the world)

```{r}
library(r2pmml)
r2pmml(model, "classification_rf.pmml")
```

Predict the values (so that I can compare the predictions)

```{r}
library(dplyr)

with_predicted_value <- occupancy %>%
  mutate(PredictedOccupancy = predict(model, occupancy))
```

Save everything to a csv (that's what I'm using on the sample application)

```{r}
library(readr)

with_predicted_value %>%
  write_csv('classification_rf_prediction.csv')
```