---
title: "Regression"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
load('math_students.data') # dataset available at http://archive.ics.uci.edu/ml/datasets/Student+Performance
```

Building a random forest for regressions... Predicting the final grade on math based on the other variables. Using 5-fold cross validation just because we can.

```{r}
library(caret)

model <- train(
  G3 ~ .,
  tuneLength = 1,
  data = math_students, method = "rf",
  trControl = trainControl(method = "cv", number = 5, verboseIter = TRUE)
)
```

This is the fun part (you need to have JAVA installed on your machine for `r2pmml` to work)

```{r}
library(r2pmml)
r2pmml(model, "regression_rf.pmml")
```

And volà, we have our PMML file. Now let's add a column with the predictions here so that we can compare them with what we get on C#

```{r}
library(dplyr)

with_predicted_value <- math_students %>%
  mutate(PredictedG3 = predict(model, math_students))
```

Store this in a CSV

```{r}
library(readr)

with_predicted_value %>%
  write_csv('regression_rf_prediction.csv')
```
